---
title: "Application: Testing theories of agenda-setting issue ownership using legislators’ Facebook posts"
author: Pablo Barbera
date: June 28, 2017
output: html_document
---

The file `data/congress-facebook.rdata` contains a data frame with the Facebook posts of all current Members of Congress, with row corresponding to a different document, after collapsing all the Facebook posts from a single member into only one character string.

We're going to run LDA to explore the different topics that Members of Congress discuss on Facebook, and whether there is variation across different characteristics, such as party and chamber.

You can skip to the end of this script if you want to see how I collected and cleaned the data, but for now let's jump straight to the topic modeling part:

```{r}
load("data/congress-facebook.rdata")
nrow(posts)
str(posts)
```

Creating the document-feature matrix in quanteda:

```{r}
library(quanteda)
fbcorpus <- corpus(posts$text)
cdfm <- dfm(fbcorpus, remove=stopwords("english"), verbose=TRUE,
               remove_punct=TRUE, remove_numbers=TRUE)
cdfm <- dfm_trim(cdfm, min_docfreq = 2, verbose=TRUE)

# we now export to a format that we can run the topic model with
dtm <- convert(cdfm, to="topicmodels")
```

And now we can run the topic model

```{r eval=FALSE}
# estimate LDA with K topics
library(topicmodels)
K <- 50
lda <- LDA(dtm, k = K, method = "Gibbs", 
                control = list(verbose=25L, seed = 123, burnin = 100, iter = 500))

save(lda, file="backup/lda-output.Rdata")
```

The code above will take some time, so I already ran it before and put it in the backup folder. Let's start looking at the results...

```{r}
library(topicmodels)
load("backup/lda-output.Rdata")
terms(lda)
# top 10 words associated to each topic
trms <- t(terms(lda, k=10))
# some topics are easy to identify
trms[6,] # media appearances
trms[15,] # supreme court nomination
trms[17,] # repealing obamacare
trms[18,] # foreign policy
trms[32,] # budgetary issues?
trms[33,] # energy policy
trms[44,] # Trump-Russia investigation
trms[46,] # town halls
trms[49,] # legislative terms
# but many others appear to simply refer to states
trms[1,]
trms[2,]
# so probably we would want to clean the data to get rid of state names
```

Let's look at how often different Members of Congress mention each topic...

```{r}
# matrix with topic distributions
mat <- lda@gamma
dim(mat)
mat[1, 1:50]
# i.e.: Member of Congress 1 is talking 16.9% of the time about Topic 26

# who is the Member of Congress that talks more about...
# immigration?
posts$name[which.max(mat[,44])] # Trump-Russia
posts$name[which.max(mat[,17])] # repealing obamacare
# northwest?
posts$name[which.max(mat[,1])]
# supreme court nomination
posts$name[which.max(mat[,15])]

# looking at differences across parties
rep.props <- apply(lda@gamma[posts$party=="Republican",], 2, mean)
dem.props <- apply(lda@gamma[posts$party=="Democrat",], 2, mean)
ratio <- rep.props / (dem.props + rep.props)

# % of topic usage by party
ratio[15] # supreme court nomination
ratio[17] # repealing obamacare
ratio[18] # foreign policy
ratio[32] # budgetary issues?
ratio[33] # energy policy
ratio[44] # Trump-Russia investigation
```



And now, here's how I collected and cleaned the data.

First of all, let's scrape the dataset with the social media accounts of Members of Congress.

```{r eval=FALSE}
scrapeCongressData <- function(){
  ## Downloading Congress data
  txt <- httr::content(httr::GET(paste0("https://raw.githubusercontent.com/unitedstates/",
                            "congress-legislators/master/legislators-current.yaml")), 'text')
  congress <- yaml::yaml.load(txt)
  congress <- data.frame(
    id = unlistCongress(congress, c('id', 'thomas')),
    bioid = unlistCongress(congress, c('id', 'bioguide')),
    name = unlistCongress(congress, c('name', 'official_full')),
    gender = unlistCongress(congress, c('bio', 'gender')),
    type = unlist(lapply(congress, function(x)
      x$terms[[length(x$terms)]]$type)),
    party = unlist(lapply(congress, function(x)
      x$terms[[length(x$terms)]]$party)),
    stringsAsFactors=F)
  ## Downloading List of Social Media Accounts
  txt <- httr::content(httr::GET(paste0("https://raw.githubusercontent.com/unitedstates/",
                            "congress-legislators/master/legislators-social-media.yaml")), 'text')
  sm <- yaml::yaml.load(txt)
  sm <- data.frame(
    bioid = unlistCongress(sm, c('id', 'bioguide')),
    twitter = unlistCongress(sm, c('social', 'twitter')),
    facebook = unlistCongress(sm, c('social', 'facebook')),
    youtube = unlistCongress(sm, c('social', 'youtube')),
    stringsAsFactors=F)
  ## merging
  df <- merge(congress, sm, all.x=TRUE)
  return(df)
}


unlistCongress <- function(lst, field){
  if (length(field)==1){
    notnulls <- unlist(lapply(lst, function(x) !is.null(x[[field]])))
    vect <- rep(NA, length(lst))
    vect[notnulls] <- unlist(lapply(lst, '[[', field))
  }
  if (length(field)==2){
    notnulls <- unlist(lapply(lst, function(x) !is.null(x[[field[1]]][[field[2]]])))
    vect <- rep(NA, length(lst))
    vect[notnulls] <- unlist(lapply(lst, function(x) x[[field[1]]][[field[2]]]))
  }
  return(vect)
}

congress <- scrapeCongressData()

```

And this is a copy of the file I downloaded...

```{r eval=FALSE}
congress <- read.csv("data/congress-social-media.csv", stringsAsFactors=F)
```


Keeping only members of congress with FB accounts

```{r eval=FALSE}
table(is.na(congress$facebook))
congress <- congress[!is.na(congress$facebook),]
```

Collecting Facebook page data

```{r eval=FALSE}
library(Rfacebook)
fb_oauth <- "YOUR_TOKEN_HERE"
# get yours from: https://developers.facebook.com/tools/explorer/

# list of accounts
accounts <- congress$facebook

# removing those already downloaded
accounts.done <- list.files("data/facebook")
accounts.left <- accounts[tolower(accounts) %in% tolower(gsub(".csv", "", accounts.done)) == FALSE]

# loop over accounts
for (account in accounts.left){
    message(account)

    # download page data (with error handling)
    error <- tryCatch(df <- getPage(account, token=fb_oauth, n=5000, since='2017/01/01',
                                    reactions=FALSE, api="v2.9"),
    	error=function(e) e)
    if (inherits(error, 'error')){ next }
    
    ## cleaning text from \n (line breaks)
    df$message <- gsub("\n", " ", df$message)

    ## save page data csv format
    write.csv(df, file=paste0("data/facebook/", account, ".csv"),
        row.names=F)
}

```

Merging text from Facebook pages into a single data frame where all posts are collapsed into a single string.

```{r eval=FALSE}
accounts <- sort(gsub(".csv", "", list.files("data/facebook")))
congress <- read.csv("data/congress-social-media.csv", stringsAsFactors=F)
congress <- congress[congress$facebook %in% accounts,]
congress <- congress[order(congress$facebook),]

posts <- data.frame(
	text = "",
	account = accounts,
	name = congress$name,
	party = congress$party,
	type = congress$type,
	gender = congress$gender, stringsAsFactors=F )

for (account in accounts){
	message(account)
	d <- read.csv(paste0("data/facebook/", account, ".csv"), 
		stringsAsFactors=F)
	posts$text[posts$account==account] <- paste(d$message, collapse=" ")
}

nrow(posts)
save(posts, file="data/congress-facebook.rdata")
```

